\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvcolor{blue}
\moderncvstyle{classic}

\usepackage[maxbibnames=99,defernumbers=true,sorting=ydnt]{biblatex}
\nocite{*}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\input{personaldata.tex}
% \bibliography{publications}
\addbibresource{publications.bib}

\setlength{\hintscolumnwidth}{3cm}

\makeatletter
\name{Gianluca}{Brian}
\title{Curriculum Vitae}
\email{\@@@email}
% \phone[mobile]{\@@@phone}
\extrainfo{
    Date of birth: 05/06/1994
}
\social[github][github.com/mclytar]{github.com/mclytar}
\makeatother

\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother

\def\pplus{\texttt{++}}
\def\sharp{\texttt{\#}}

\renewcommand{\refname}{Research activities and publications}
\DefineBibliographyExtras{english}{\let\finalandcomma=\empty}
\newcommand{\pubitem}[1]{
    \cvitem{\citefield{#1}{year}}{\textbf{\citefield{#1}{title}} (with \citename{#1}{author}), in \textit{\citefield{#1}{booktitle} } }
}

\makeatletter
\newcommand{\citesinthissection}[1]{\xdef\@totalcites{#1}}
% https://tex.stackexchange.com/q/123805/5764
\defbibenvironment{bibliography}
  {\list
     {\printtext[labelnumberwidth]{% label format from numeric.bbx
        \printfield{prefixnumber}%
        \number\numexpr\@totalcites-\abx@field@labelnumber+1\relax}}
     {\setlength{\topsep}{0pt}% layout parameters from moderncvstyleclassic.sty
      \setlength{\labelwidth}{\hintscolumnwidth}%
      \setlength{\labelsep}{\separatorcolumnwidth}%
      \leftmargin\labelwidth%
      \advance\leftmargin\labelsep}%
      \sloppy\clubpenalty4000\widowpenalty4000}
  {\endlist}
  {\item}
\makeatother

\begin{document}
    \makecvtitle
    \section{Research interests}
    \cvitem{}{
        I am interested in theoretical and applied cryptography, with particular focus on side channel attacks and prevention.
        Current topics include: information theory, leakage and fault resilience, constructive cryptography, modular designs.
    }

    \section{Current position}
    \cventry{Jun 25 -- Now}{Postdoctoral Researcher}{TU Darmstadt}{Germany}{}{
        Supervisor: \emph{Prof. Sebastian Faust}
    }

    \section{Previous positions}
    \cventry{Jun 23 -- May 25}{Postdoctoral Researcher}{ETH Zurich}{Switzerland}{}{
        Supervisor: \emph{Prof. Ueli Maurer}
    }
    \cventry{Mar 23 -- May 23}{Scientific Assistant}{ETH Zurich}{Switzerland}{}{
        Supervisor: \emph{Prof. Ueli Maurer}
    }
    \cventry{Nov 21 -- Nov 22}{Visiting Researcher}{University of Warsaw}{Poland}{}{
        Supervisor: \emph{Prof. Stefan Dziembowski}
    }

    \section{Education}
    \cventry{Nov 19 -- Jan 23}{Ph.D. in Computer Science}{Sapienza University of Rome, Italy}{}{}{
        Final grade: \emph{pass (with honors)}\\
        Thesis title: \emph{Non-malleable secret sharing against joint tampering attacks}\\
        Supervisor: \emph{Prof. Daniele Venturi}
    }
    \cventry{Sep 16 -- Jul 19}{M.Sc. in Mathematics}{Sapienza University of Rome, Italy}{}{}{
        Final grade: \emph{106/110}\\
        Thesis title: \emph{Non-malleable Secret Sharing under Selective Partitioning}.\\
        Advisors: \emph{Prof. Claudia Malvenuto and Prof. Daniele Venturi}.
    }
    \cventry{Sep 13 -- Dec 16}{B.Sc. in Mathematics}{Sapienza University of Rome, Italy}{}{}{
        Final grade: \emph{105/110}\\
        Thesis title: \emph{Complexity and public key cryptosystems}.\\
        Advisor: \emph{Prof. Alessandro D'Andrea}.
    }

    \section{Ph.D. Schools attended}
    \cventry{Apr 22}{IACR-Crossing School}{La Valletta, Malta}{}{}{
        Main topic: \emph{Combinatorial Techniques in Cryptography}
    }
    \cventry{Jul -- Aug 21}{MSRI Summer Graduate School}{Virtual on Zoom/Sococo}{}{}{
        Main topic: \emph{Foundations and Frontiers of Probabilistic Proofs}
    }
    \cventry{Feb 21}{BIU Winter School on Cryptography}{Virtual on Zoom}{}{}{
        Main topic: \emph{Cryptography in a Quantum World}
    }
    \cventry{Feb 20}{BIU Winter School on Cryptography}{Tel Aviv, Israel}{}{}{
        Main topic: \emph{Information Theoretic Cryptography}
    }

    \section{Teaching Experience}
    \cventry{Spring 2025}{Co-organizer and student supervisor}{Current Topics in Cryptography Seminar}{ETH Zurich}{}{}
    \cventry{Fall 2024}{Teaching Assistant}{Discrete Mathematics}{ETH Zurich}{}{}
    \cventry{Spring 2024}{Student supervisor}{Current Topics in Cryptography Seminar}{ETH Zurich}{}{}
    \cventry{Fall 2023}{Teaching Assistant}{Discrete Mathematics}{ETH Zurich}{}{}
    \cventry{Spring 2023}{Student supervisor}{Current Topics in Cryptography Seminar}{ETH Zurich}{}{}

    \section{Talks}
    \subsection{Publications at conferences}
    \cventry{May 24}{From Random Probing to Noisy Leakages Without Field-Size Dependence}
    {Advances in Cryptology --- EUROCRYPT 2024: 43th Annual International Conference on the Theory and Applications of Cryptographic Techniques}
    {Zurich, Switzerland}
    {}{}
    \cventry{Nov 21}{Continuously Non-malleable Secret Sharing: Joint Tampering, Plain Model and Capacity}
    {Theory of Cryptography: 19th International Conference, TCC 2019}
    {Raleigh, NC, USA (online talk)}
    {}{}
    \cventry{Oct 21}{The Mother of All Leakages: How to Simulate Noisy Leakages from Bounded Leakage (Almost) for Free}
    {Advances in Cryptology --- EUROCRYPT 2021: 40th Annual International Conference on the Theory and Applications of Cryptographic Techniques}
    {Zagreb, Croatia}
    {}{}
    \cventry{Aug 20}{Non-malleable Secret Sharing against Bounded Joint-Tampering Attacks in the Plain Model}
    {Advances in Cryptology --- CRYPTO 2020: 40th Annual International Cryptology Conference}
    {Virtual on Zoom}
    {}{}
    \cventry{Dec 19}{Continuously Non-malleable Secret Sharing for General Access Structures}
    {Theory of Cryptography: 17th International Conference, TCC 2019}
    {Nuremberg, Germany}
    {}{}

    \subsection{Invited talks}
    \cventry{Oct 24}{An overview of Side-Channel Security}
    {Collaboration event with TU Darmstadt and University of Warsaw for the Copernicus Award celebration}
    {Berlin, Germany}
    {}{}
    \cventry{Aug 24}{From Random Probing to Noisy Leakages Without Field-Size Dependence}
    {Conference on Information Theoretic Cryptography (ITC 2024)}
    {Palo Alto, CA, USA}
    {}{}
    \cventry{Oct 20}{Leakage-Resilient Non-Malleable Secret Sharing}
    {Seminar at De Cifris Schola Latina}
    {Virtual on Google Meet}
    {}{}

    \section{Other activities}
    \subsection{Memberships}
    \cvitem{2019 -- Now}{IACR Membership}
    \subsection{External reviewer}
    \cvitem{}{CRYPTO 2025, EUROCRYPT 2022, EUROCRYPT 2021}

    \section{Scientific production}

    \newrefcontext[labelprefix=c]
    \citesinthissection{6}
    \printbibliography[title={Publications in conferences},heading = subbibliography,keyword = conference]

    \newrefcontext[labelprefix=j]
    \citesinthissection{2}
    \printbibliography[title={Publications in journals},heading = subbibliography,keyword = journal]

    \newrefcontext[labelprefix=pp]
    \citesinthissection{1}
    \printbibliography[title={Preprints},heading = subbibliography,keyword = preprint]

    \newrefcontext[labelprefix=wip]
    \citesinthissection{1}
    \printbibliography[title={Work in progress (not yet published)},heading = subbibliography,keyword = wip]

    % \pubitem{EUROCRYPT:BDF24}
    % \pubitem{AC:BFMV22}
    % \pubitem{ToSC:BFRV22}
    % \pubitem{TCC:BFV21}
    % \pubitem{EUROCRYPT:BFORSSV21}
    % \pubitem{CRYPTO:BFOSV20}
    % \pubitem{TCC:BFV19}

    \section{Computer skills}
    \cvitem{Programming Languages}{
        Proficient in Rust.
        Good knowledge of C, C\pplus{}, Assembly (x86, ARM), and the GNU GCC Toolchain.
        Basic knowledge of Visual Basic, Python, CUDA C, and C\sharp{}, in no particular order.
    }
    \cvitem{Typesetting}{
        \LaTeX, including TikZ and the \texttt{beamer} template for slides.
    }
    \cvitem{Software}{
        Microsoft Office suite (Word, Excel, Power Point), JetBrains CLion/RustRover/WebStorm, MS Visual Studio, MS Visual Studio Code, Git, Powershell.
    }
    \cvitem{Misc.}{
        Embedded Systems development (including experience with Arduino and ChipWhisperer).
    }
    \cvitem{Operating systems}{
        Windows, Linux.
    }

    \section{Languages}
    \cvitem{}{
        Italian (Mother tongue),
        English (C1, self-assessed),
        Polish (A2, self-assessed),
        German (A2, \emph{certified})
    }

    \section{Spare time activities}
    \cvitem{Mathematics}{
        I participated in several mathematics challenges and olympic games (both alone and in team) during my high school years.
    }
    \cvitem{Hobbies}{
        Videogames: I enjoy factory-building and city-building videogames, as well as racing and flight simulation.
    }
    \cvitem{}{
        Misc.: I am designing a computer based on the Intel 8086 CPU.
        I studied the official documentation, the patent, and the reverse-engineering information about the 8086, understanding
        its microarchitecture, the microcode, and the internal states, which I am using to build a simulator for the 8086.
        I also studied the VGA standards for the video interface, learned to use CAD software to design the motherboard,
        and designed a programmer for the EEPROM with Arduino.
        Future tasks involve the development of a custom memory-safe language with a lightweight compiler that I will then use
        to write the BIOS and the operating system.
    }
    \cvitem{Interests}{
        I am deeply interested in mathematics and science in general:
        I love to see the beauty of mathematical abstraction and to understand how our universe works.
    }

\end{document}